Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-04-26 Manuscript/PLoSONEresponse/response.tex

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
The matrix [...] was generated [...] using the HKY model with random base frequencies (sampled from a uniform probability distribution bounded between 0 and 1 with the total frequency for the four bases equal to 1)[...]
\end{minipage}

%-------------

\textcolor{blue}{Do the simulations apply ascertainment biases as described by Lewis' Mkv (2001) model? It seems like they should... At minimum, the point should be discussed.}

We are not entirely sure if the reviewers refers to a sampling bias or to the problem link to constant characters described in Lewis (2001) (acquisition bias). If the reviewers are referring to the second (acquisition bias), both phylogenetic inference software we used (RAxML and MrBayes) are correcting for the this bias (-K MK  see Supplementary information 1 for the full list of commands). Also, the effect of the acquisition bias is to inflate branch length which is an aspect of the phylogeny we didn't explored in this study (focusing on topology). See response below to the comment ``\textit{The use of Mk rather than Mkv makes the study less relevant to real data analyses.}".

@@

We would like to emphasize that in this study we focused on the effect of missing data in the morphological part of the matrix on topology only.The choice of the following priors (``exponential prior on the shape of the gamma distribution of $\alpha$ = 0.5 for both partitions" (line 228) and the ``transition/transversion ratio prior of two sampled from a strong beta 229 distribution ($\beta$(80,40))" (line 229)) affected mainly the molecular part of the matrix that remains constant (gamma distribution and transition/transversion ratio) and where a minor part of the MCMC sampler (2.17\% of move probability for the three priors). Therefore we are confident that the topology is not affected allowing us to explore the effect of missing morphological data on topology as well as reducing our computational time to a realistic 1.5 CPU century.

%-------------

\textcolor{blue}{line 254: RF measures the difference between the number of clades and the twice number of shared clades across two trees. The statement that it ``measures the number of shared clades across two trees" should be revised.}

We changed the following sentence:

Lines 254 to 255 in the previously submitted manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
The Robinson-Foulds distance, or ``path difference", measures the number of shared clades across two trees.
\end{minipage}

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
The Robinson-Foulds distance, or ``path difference", measures the difference between the number of clades and the twice number of shared clades across two trees.
\end{minipage}

@@

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
The Robinson-Foulds distance, or ``path difference", measures the difference between the number of clades and the twice number of shared clades across two trees.
\end{minipage}

%-------------

\textcolor{blue}{line 258: RF is 0 (not 1) when the trees are identical. It's maximum (for 2 rooted binary trees) is 2(n-2) not n-2.}

We changed the following sentence:

Lines 257 to 259 in the previously submitted manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
This metric is bounded between one, when the two trees are identical, and $n-2$ (for two trees with $n$ taxa) when there is no shared clade in the two trees.
\end{minipage}

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
This metric is bounded between zero, when the two trees are identical, and $2(n-2)$ (for two trees with $n$ taxa) when there is no shared clade in the two trees.
\end{minipage}

%%%%%%%%%%%%%%%%%
%CHECK in Soltis!
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%
%CHECK in Soltis!
%%%%%%%%%%%%%%%%%

%-------------

\textcolor{blue}{The ``scaling" to produce the Normalized RF ``distance" is confusing. It is also inverting the sign of the distance, so it has become a measure of similarity.}

We clarified the scaling method as follow:

Lines 262 to 270 in the previously submitted manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
We normalised this metric by dividing the Robinson-Foulds distance by the mean Robinson-Foulds distance from 1000 random tree comparisons (Bogdanowicz et al. 2012). This allows us to compare the metric for any number of taxa by scaling it with the expected value of the metric when comparing two random trees (see Supporting Information S2: Tree Comparisons for the calculation details). Therefore, when the Normalised Robinson-Foulds distance between two trees is equal to one, the trees are identical; if the distance is equal to zero, the trees are no more different than expected by chance; finally if the distance is less than zero, the trees are more different than expected by chance.
\end{minipage}

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
We normalised this metric following Bogdanowicz \textit{et al.} (2012)'s Normalised Tree Similarity (NTS) method. This methods scales %not sure if scale here?
any tree comparison metric using the mean distance between 1000 random trees (see Supporting Information S2: Tree Comparisons for the calculation details). This method is a generalisation of the topological accuracy method (Price \textit{et al.} 2010) allowing to compare topological differences between any tree with any tree comparison metric. In practice when the Normalised Robinson-Foulds distance between two trees is equal to one, the trees are identical; if the distance is equal to zero, the trees are no more different than expected by chance; finally if the distance is less than zero, the trees are more different than expected by chance.
\end{minipage}

@@

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
We normalised this metric following Bogdanowicz \textit{et al.} (2012)'s Normalised Tree Similarity (NTS) method. This methods scales %not sure if scale here?
any tree comparison metric using the mean distance between 1000 random trees (see Supporting Information S2: Tree Comparisons for the calculation details). This method is a generalisation of the topological accuracy method (Price \textit{et al.} 2010) allowing to compare topological differences between any tree with any tree comparison metric. In practice when the Normalised Robinson-Foulds distance between two trees is equal to one, the trees are identical; if the distance is equal to zero, the trees are no more different than expected by chance; finally if the distance is less than zero, the trees are more different than expected by chance.
\end{minipage}

%-------------

\textcolor{blue}{line 275: why isn't the upper bound of the triples distance n choose 3 (instead of n choose 4). I think you got the formula from an unrooted quartet distance.}

We changed the following sentence:

Lines 274 to 275 in the previously submitted manuscript:

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
It is bounded between zero when the two trees are identical and $\binom{n}{4}$ (for two trees with $n$ taxa) when there is no shared taxa/clade position in the two trees.
\end{minipage}

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
It is bounded between zero when the two trees are identical and $\binom{n}{3}$ (for two trees with $n$ taxa) when there is no shared taxa/clade position in the two trees.
\end{minipage}

%%%%%%%%%%%%%%%%%
%CHEK in Soltis!
%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%
%CHEK in Soltis!
%%%%%%%%%%%%%%%%%

%-------------

\textcolor{blue}{Using the BC stat may be similar in spirit to using a t-test, but it is not equivalent.}

We clarified this point in the text as well as in the figures 2 and 3 captions (``equivalent" $->$ ``similar"):

@@

\hfill\begin{minipage}{\dimexpr\textwidth-1cm}
Note that this is similar to performing a two-sided t-test for comparing two distribution.
\end{minipage}

%-------------

\textcolor{blue}{Figure 3: B is confusing. If both curves are probability distributions, then they both have to integrate to 1. So B(y) can't cover just a subset of the area covered by B(x).}

%I'm not sure how to fix that comment. The figure caption says (first sentence!) : "A and B are distributions of tree similarity metrics (Normalised Robinson-Foulds or Normalised Triplets distances) for any combination of missing data parameters (e.g. ML = 10%,MF = 50%, MC = 75%)." Should I make it super clear by writing : "A and B are distributions of tree similarity metrics (not probability distributions, or roller coasters plans)" ?

@@

%-------------

\textcolor{blue}{``Combined effect of missing data parameters" section ANOVA or multiple regression are the appropriate analyses to tease apart multiple interacting factors. Here the authors opt to describe results without statistical tests, which is disappointing.}

This comment links back to the reviewer's misconception of the term ``statistics" and suspicions. ANOVA or multiple regression analysis might the appropriate analyses in some cases but we believe it isn't here. In our analysis, we made the methodological choice to compare tree similarity distributions that are: not continuous distributions; bounded at 1; not always normal (both the distributions and the residuals) and sometimes multi-modal. Therefore, we choose not to use classical ``statistics" methods such as ANOVA or multiple regression because these methods could simply not be applied to our data set.
%Not comparing means, non normal distributions. And non-parametric version (e.g. Kruskal Wallis) not approriate either.

@@

\textcolor{blue}{line 398: ``mMthods" $->$ ``Methods"}

We fixed this typo.

\textcolor{blue}{line 420: contra the statement here, a consensus collapsing to a polytomy will affect the RF distance (could go up or down, but it will change).}

%To

This does not decrease the 420
Normalised Robinson-Foulds distance, because clades are conserved, but decreases the 421
Normalised Triplets distance because the fossils act as wildcard taxa. 422

### 2015-04-27 Manuscript/PLoSONEresponse/response.tex

\begin{letter}{}

RE: PLOS ONE Decision: PONE-D-15-05911 - [EMID:ffa50492e76c2059]

Dear Dr Fontaneto

Please find enclosed our resubmission of our manuscript ``Effects of missing data on topological inference using a Total Evidence approach". We include below details of how we have dealt with the reviewer's comments.

We would however, like to draw your attention to a couple of points. Firstly, while we understand the difficulties of obtaining reviewers for papers, we were very disappointed to have the previous decision made based on just one review. As pointed out in your email, this reviewer responded immediately. We suspect they rushed their assessment because they make several comments about our paper that are completely incorrect, and would have been noticed in a thorough reading of the manuscript.

%For example, the reviewer says that our data are not available when we clearly state on @@@[page and lines] that all the data are deposited in figshare @@@[link]. We suspect that had a second reviewer been found the decision might have been different. % TG: ok, this part somehow was in the SystBiol manuscript as a header part of the supplementary (1 file with three appendices) and I forgot to included somewhere in the manuscript or the supplementary in last submission (3 files). See the "OnlineAppendices" file in the GitHub folder. However, references to the GitHub page is given in the 1 supplementary material, but I assume it's a bit weak... My bad.

%We can maybe moan about the reviewer not reading carefully few things such as the comment on figure 3B "Figure 3: B is confusing. If both curves are probability distributions, then they both have to integrate to 1. So B(y) can't cover just a subset of the area covered by B(x)." where it seems he just didn't properly read the caption or about the Bhattacharya where he didn't read that we applied it because we're not comparing the means... But it's a bit weaker.

%In general I feel actually bad for some comments (i.e. typos in the equations etc...) and will remember to check more thoroughly next time.

@@

%Change to "affect less" or something like that.

%-------------

\textcolor{blue}{-------------------------}

%So for the part about the tree comparisons (RF and Triplets, I think we can just remove the whole thing since it's not especially useful...)

@@

We cited the reference (Bogdanowicz 2012) of the method.

%-------------

\textcolor{blue}{The NTS can only -infinity for distances that have the property that the mean distance between random Yule trees is 0. This is not true of either distance metric here. So the real range of values is (mean-max)/mean for both the RF and triples distance.}

As clarified in the new manuscript (lines @@@), the NTS is a generalisation of the topological accuracy method (Price \textit{et al.} 2010 PLoS ONE) and is therefore not specialised for the RF or the Triples distance.

### 2015-04-28 Manuscript/PLoSONESubmission/OnlineAppendices-LaTeXSuppFiles/SupportingInformation2.tex

%\section{Supplementary material Section 2}

\subsection{Robinson-Foulds distance}
Robinson-Foulds distance (\textit{RF}; \citealp{RF1981}), or "path difference", measures the number of shared clades across two trees. The metric reflects the distance between the distributions of tips among clades in the two trees \citep{RF1981} and can be expressed as:
\begin{equation}
RF_{x,y} = N_{x} + N_{y} - 2C_{x,y}
\end{equation}
where $C_{x,y}$ is the number of clades in common in the two trees. $C$ is equal to one if the two trees have the same $n$ taxa; and $C = n-2$ when none of the $n$ taxa are shared between the trees. This metric is more sensitive to taxon displacement than Triplets distance (i.e. if one taxon moves out of a clade, then the clades are no longer considered similar; \citet{critchlowthe1996,johnson1998,wiensmissing2003}). The minimal value of $C$ is equal to 1 if the two trees have the same n taxa; the maximal value in $C = n-2$. For a fully unresolved tree (star tree) $N$=1 and for a fully resolved tree (binary tree) $N = n-2$. The minimal and maximal topological distance for taxa is:
\begin{equation}
RF_{min} = 1 + 1 - 2C_{x,y}
\end{equation}
and:
\begin{equation}
RF_{max} = 2(n-2)-2
\end{equation}
One can then rescale \textit{RF.scaled} by using the maximal and minimal value for any $n$ taxa:
\begin{equation}
RF.scaled_{x,y} = \frac{RF_{x,y}-RF_{max}}{RF_{max}}
\end{equation}
This metric is more sensitive to taxa displacement than the Triplets distance \citep{critchlowthe1996,johnson1998,wiensmissing2003} and therefore a low value will show a good clade conservation between two trees and a high value will show a bad recovery of common clades.

\subsection{Triplets distance details ($T_{x,y}$)}
Triplets distance ($T_{x,y}$; \citealp{dobson1975triplets}) measures the number of sub-trees made up of three taxa (triplets) that differ between two given trees. Each triplet can be written as $I_{ijk}$=(\textit{ijk}). Where $I_{ijk}$ is equal to zero if the the two triplets (\textit{ijk}) are the same in the two trees otherwise $I_{ijk}$ is equal to one. For any rooted binary tree there are only three possible combinations for each triplet: ((\textit{j},\textit{k}),\textit{i});, ((\textit{i},\textit{k}),\textit{j}); and ((\textit{i},\textit{j}),\textit{k}); \citep{johnson1998}. If the trees used are not fully binary, a fourth triplet combination is possible: (\textit{i},\textit{j},\textit{k}). We can calculate the triplet distance between two trees, $S_n$, as:
\begin{equation}
S_n = \sum_{ijk} I_{ijk}
\end{equation}
where:
\begin{equation}
\sum_{ijk} = \binom{n}{4} = \frac{n!}{4!(n-4)!}
\end{equation}
and where \textit{n} is the total number of taxa in both trees (modified from \citet{critchlowthe1996}). If $S_n$ = 0, the trees are identical; when $S_n$ = $\binom{n}{4}$, the trees are as different as possible (i.e. every taxon has a different placement in the two trees). Because the possible number of triplets per clade is a finite number, the probability of two random trees with the same $n$ taxa to have the same triplet is:
\begin{equation}
P({I_{ijk}}=0) = \frac{1}{4}
\end{equation}
Therefore one can calculate the probability of two random trees having the same triplets: 
\begin{equation}
P({S_{n}}=0) = \sum_{ijk} P_{I_{ijk}=0}
\end{equation}
\begin{equation}
P({S_{n}}=0) = \frac{n!}{4(3!(n-3)!}
\end{equation}
and in the same way:
\begin{equation}
P({S_{n}}=1) = \frac{3n!}{4(3!(n-3)!}
\end{equation}

\subsection{Normalised Tree Similarity}
For any tree with \textit{n} taxa compared using a tree distance metric $m$, Normalized Tree Similarity, $NTS_m$ \citep{Bogdanowicz2012}, represents the similarity score for the two trees given the expected distance between two random Yule trees with $n$ taxa. If $\bar{d}_{m,n}$\textit{(rand)} is the average distance between two random Yule trees with $n$ taxa and $d_{m,n}$\textit{(x,y)} the distance between the two trees \textit{x} and \textit{y} each containing $n$ taxa, then:
\begin{equation}
NTS_{m,n}(x,y)=\frac{\bar{d}_{m,n}(rand) - d_{m,n}(x,y)} {\bar{d}_{m,n}(rand)}
\end{equation}
\textit{NTS} ranges from one to -$\infty$.
For any $m,n$, when $NTS$ = 1, the trees are identical, when \textit{NTS} = 0 the trees are no more different than expected by chance, and when $NTS$ $<$ 0, the trees are more different than expected when comparing two random trees.

We used the NTS method to scale all the Robinson Foulds and Triplets distances calculated in our analyses, using the TreeCmp java script \citep{Bogdanowicz2012}.

% NC: Not sure this bit is needed
%We compared 1000 randomly generated trees to obtain the mean comparison value $\bar{d}_{m,n}$\textit{(rand)}. We randomly generated two sets of 1000 trees of \textit{n} taxa using the rmtree function of ape package (v3.0-11 \citet{paradisape:2004}) that generates a given number of random Yule trees. We calculated the $\bar{d}_{m,n}$\textit{(rand)} value using an approach similar to the RPCBTC (described below) by performing 1000 random pairwise comparisons using the TreeCmp java script \citep{Bogdanowicz2012}.

\subsection{Bhattacharyya Coefficient}
The Bhattacharyya Coefficient calculates the probability of overlap of two distributions \citep{Bhattacharyya}. When it is equal to zero, the probability of overlap of the distributions is also zero, and when it is equal to one, the two distributions are entirely overlapping. It forms an elegant and easy to compute continuous measurement of the probability of similarity between two distributions. The coefficient is calculated as the sum of the square root of the relative counts shared in \textit{n} bins among two distributions.
\begin{equation}
\text{Bhattacharyya Coefficient}=\sum_{i=1}^{n} \sqrt{{\sum{a_i}}\times{\sum{b_i}}}
\end{equation}
where
\begin{equation}
\sum{a_i}=\frac{\text{Number of counts in bin \textit{i} for the distribution \textit{a}}}{\text{Total number of counts for the distribution \textit{a}}}
\end{equation}
and
\begin{equation}
\sum{b_i}=\frac{\text{Number of counts in bin \textit{i} for the distribution \textit{b}}}{\text{Total number of counts for the distribution \textit{b}}}
\end{equation}
The precision of the Bhattacharyya Coefficient is directly related to the number of bins, $n$. If $n$ is low, the overlap will be overestimated and if $n$ is too high, the overlap will be underestimated. In this analysis, we determined the number of bins using Silverman's rule of thumb which states that $n$ should be 0.9 times the minimum of the standard deviation and the interquartile range of the distribution, divided by 1.34 times the sample size of the distribution to the negative one-fifth power (bw.nrd0() function in R; \citet{silverman1986density}).

>>>>

\documentclass[12pt,letterpaper]{article}

%Packages
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\pagenumbering{arabic}

%Pagination style and stuff
\linespread{2}
\raggedright
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0} 
\renewcommand{\section}[1]{%
\bigskip
\begin{center}
\begin{Large}
\normalfont\scshape #1
\medskip
\end{Large}
\end{center}}
\renewcommand{\subsection}[1]{%
\bigskip
\begin{center}
\begin{large}
\normalfont\itshape #1
\end{large}
\end{center}}
\renewcommand{\subsubsection}[1]{%
\vspace{2ex}
\noindent
\textit{#1.}---}
\renewcommand{\tableofcontents}{}

\begin{document}

\section{Supporting Information S2: Tree Comparisons}

\subsection{Robinson-Foulds distance}
Robinson-Foulds distance (\textit{RF} \cite{RF1981}), or "path difference", measures the number of shared clades across two trees. The metric reflects the distance between the distributions of tips among clades in the two trees \cite{RF1981} and can be expressed as:
\begin{equation}
RF_{x,y} = N_{x} + N_{y} - 2C_{x,y}
\end{equation}
where $C_{x,y}$ is the number of clades in common in the two trees. $C$ is equal to one if the two trees have the same $n$ taxa; and $C = n-2$ when none of the $n$ taxa are shared between the trees. This metric is more sensitive to taxon displacement than Triplets distance (i.e. if one taxon moves out of a clade, then the clades are no longer considered similar \cite{critchlowthe1996,johnson1998,wiensmissing2003}). The minimal value of $C$ is equal to 1 if the two trees have the same n taxa; the maximal value in $C = n-2$. For a fully unresolved tree (star tree) $N$=1 and for a fully resolved tree (binary tree) $N = n-2$. The minimal and maximal topological distance for taxa is:
\begin{equation}
RF_{min} = 1 + 1 - 2C_{x,y}
\end{equation}
and:
\begin{equation}
RF_{max} = 2(n-2)-2
\end{equation}
One can then rescale \textit{RF.scaled} by using the maximal and minimal value for any $n$ taxa:
\begin{equation}
RF.scaled_{x,y} = \frac{RF_{x,y}-RF_{max}}{RF_{max}}
\end{equation}
This metric is more sensitive to taxa displacement than the Triplets distance \cite{critchlowthe1996,johnson1998,wiensmissing2003} and therefore a low value will show a good clade conservation between two trees and a high value will show a bad recovery of common clades.

\subsection{Triplets distance details ($T_{x,y}$)}
Triplets distance ($T_{x,y}$ \cite{dobson1975triplets}) measures the number of sub-trees made up of three taxa (triplets) that differ between two given trees. Each triplet can be written as $I_{ijk}$=(\textit{ijk}). Where $I_{ijk}$ is equal to zero if the the two triplets (\textit{ijk}) are the same in the two trees otherwise $I_{ijk}$ is equal to one. For any rooted binary tree there are only three possible combinations for each triplet: ((\textit{j},\textit{k}),\textit{i});, ((\textit{i},\textit{k}),\textit{j}); and ((\textit{i},\textit{j}),\textit{k}) \cite{johnson1998}. If the trees used are not fully binary, a fourth triplet combination is possible: (\textit{i},\textit{j},\textit{k}). We can calculate the triplet distance between two trees, $S_n$, as:
\begin{equation}
S_n = \sum_{ijk} I_{ijk}
\end{equation}
where:
\begin{equation}
\sum_{ijk} = \binom{n}{4} = \frac{n!}{4!(n-4)!}
\end{equation}
and where \textit{n} is the total number of taxa in both trees (modified from \cite{critchlowthe1996}). If $S_n$ = 0, the trees are identical; when $S_n$ = $\binom{n}{4}$, the trees are as different as possible (i.e. every taxon has a different placement in the two trees). Because the possible number of triplets per clade is a finite number, the probability of two random trees with the same $n$ taxa to have the same triplet is:
\begin{equation}
P({I_{ijk}}=0) = \frac{1}{4}
\end{equation}
Therefore one can calculate the probability of two random trees having the same triplets: 
\begin{equation}
P({S_{n}}=0) = \sum_{ijk} P_{I_{ijk}=0}
\end{equation}
\begin{equation}
P({S_{n}}=0) = \frac{n!}{4(3!(n-3)!}
\end{equation}
and in the same way:
\begin{equation}
P({S_{n}}=1) = \frac{3n!}{4(3!(n-3)!}
\end{equation}

\subsection{Normalised Tree Similarity}
For any tree with \textit{n} taxa compared using a tree distance metric $m$, Normalized Tree Similarity, $NTS_m$ \cite{Bogdanowicz2012}, represents the similarity score for the two trees given the expected distance between two random Yule trees with $n$ taxa. If $\bar{d}_{m,n}$\textit{(rand)} is the average distance between two random Yule trees with $n$ taxa and $d_{m,n}$\textit{(x,y)} the distance between the two trees \textit{x} and \textit{y} each containing $n$ taxa, then:
\begin{equation}
NTS_{m,n}(x,y)=\frac{\bar{d}_{m,n}(rand) - d_{m,n}(x,y)} {\bar{d}_{m,n}(rand)}
\end{equation}
\textit{NTS} ranges from one to -$\infty$.
For any $m,n$, when $NTS$ = 1, the trees are identical, when \textit{NTS} = 0 the trees are no more different than expected by chance, and when $NTS$ $<$ 0, the trees are more different than expected when comparing two random trees.

We used the NTS method to scale all the Robinson Foulds and Triplets distances calculated in our analyses, using the TreeCmp java script \cite{Bogdanowicz2012}.

\subsection{Bhattacharyya Coefficient}
The Bhattacharyya Coefficient calculates the probability of overlap of two distributions \cite{Bhattacharyya}. When it is equal to zero, the probability of overlap of the distributions is also zero, and when it is equal to one, the two distributions are entirely overlapping. It forms an elegant and easy to compute continuous measurement of the probability of similarity between two distributions. The coefficient is calculated as the sum of the square root of the relative counts shared in \textit{n} bins among two distributions.
\begin{equation}
\text{Bhattacharyya Coefficient}=\sum_{i=1}^{n} \sqrt{{\sum{a_i}}\times{\sum{b_i}}}
\end{equation}
where
\begin{equation}
\sum{a_i}=\frac{\text{Number of counts in bin \textit{i} for the distribution \textit{a}}}{\text{Total number of counts for the distribution \textit{a}}}
\end{equation}
and
\begin{equation}
\sum{b_i}=\frac{\text{Number of counts in bin \textit{i} for the distribution \textit{b}}}{\text{Total number of counts for the distribution \textit{b}}}
\end{equation}
The precision of the Bhattacharyya Coefficient is directly related to the number of bins, $n$. If $n$ is low, the overlap will be overestimated and if $n$ is too high, the overlap will be underestimated. In this analysis, we determined the number of bins using Silverman's rule of thumb which states that $n$ should be 0.9 times the minimum of the standard deviation and the interquartile range of the distribution, divided by 1.34 times the sample size of the distribution to the negative one-fifth power (\texttt{bw.nrd0()} function in R \cite{silverman1986density}).

\bibliographystyle{plos2009}
\bibliography{Supp_Ref}

%END
\end{document}
